df <- read.csv("dat.txt", as.is=TRUE, header=T)


# Importing the libraries
```{r}
library(dplyr)
library(magrittr)
library(caret) 
library(caTools)
library(data.table)
library(ggplot2)    
library(corrplot)
library(pROC)
library(tidyverse)
library(table1)
library(finalfit)
library(knitr)
library(odds.n.ends)
library(ROCR) 
```

OSEMN Framework 
# Step 1: Obtaining Data 

```{r}
dataset <- setDT(read.csv("C:/Users/a2i/Desktop/LTU/Data Science/R final/space.csv"))
data<- as.data.frame(dataset)
```
# Step 2: Scrubbing Data
The data that we obtain will be messy.

Real data can have inconsistencies, missing values and various other forms of corruption. If it was scraped from a difficult data source, it may require tripping and cleaning up. Even clean data may require post-processing to make it uniform and consistent.

Before data cleansing, we will have to explore the data. 

# Data Exploration

```{r}
head(dataset)
```
```{r}
summary (dataset)
```


```{r}
table(dataset$Mission)
```

```{r}
table(dataset$Rocket)
```

```{r}
names(dataset)
```

```{r}
summary(data$Company)
```
# Checking null values 
```{r}
#finding the missing values 
print("Missing values in Company Column -")
sum(data$Company == "")

print("Missing values in Location Column -")
sum(data$Location == "")

print("Missing values in Date Column -")
sum(data$Date == "")

print("Missing values in Time Column -")
sum(data$Time == "")

print("Missing values in Rocket Column -")
sum(data$Rocket == "")

print("Missing values in Mission Column -")
sum(data$Mission == "")

print("Missing values in RocketStatus Column -")
sum(data$RocketStatus == "")

print("Missing values in Price Column -")
sum(data$Price == "")
```
```{r}
# since the number of missing values in Price Column is large, I will delete the Price Column using  dplyr package
 
dataset <- dataset %>% select(-c(Price))
print(dataset)
```
#Data Engineering



```{r}
library(lubridate)
library(timechange)
```


```{r}
print (dataset)
myDate = as.POSIXct(dataset$Date)
Month = format(myDate,"%m")
print(Month)
dataset <- cbind(dataset, Month) 
print(dataset)

```
```{r}
dataset$Weekday <-wday(dataset$Date)
print(dataset)

```

```{r}

class(dataset$Month)
hist(as.numeric(dataset$Month))
```
```{r}
class(dataset$Month)
hist(as.numeric(dataset$Weekday))
```

```{r}
encode_onehot <- function(x, colname_prefix = "", colname_suffix = "") {
  if (!is.factor(x)) {
      x <- as.factor(x)
  }

  encoding_matrix <- contrasts(x, contrasts = FALSE)
  encoded_data <- encoding_matrix[as.integer(x)]

  colnames(encoded_data) <- paste0(colname_prefix, colnames(encoded_data), colname_suffix)

  encoded_data
}

dataset <- cbind(datset, encode_onehot(dataset$Company))
```

```{r}
print
```
#Data Cleaning

```{r}
dataset=select(dataset, -c(Location, Datum, Detail))
```
```{r}
print(dataset)
```
#Splitting dataset
```{r}
ind = sample.split(Y = dataset2$Success, SplitRatio = 0.8)
```
#subsetting into Train data
```{r}
train = dataset2[ind,]
```
```{r}
#subsetting into Test data
test = dataset2[!ind,]
```

```{r}
dim(train)
dim(test)
```
#Making Logistic Regression Model 

```{r}
model <- glm(Success ~., family=binomial(link='logit'), data=train)
summary(model)

```

```{r}
plot(model)
```
```{r}
predict <- predict(model, 
                       test, type = "response")
predict
```
```{r}
logit = glm (Success ~., family = binomial(), data = dataset2)
logit.prob = predict(logit, type = 'response')
logit.class = ifelse (logit.prob > 0.5, '1', '0') %>% as.factor()
c_m = table (dataset2$isFraud, logit.class)
c_m

```

#ROC - AUC Curve
```{r}
logistic_predictions <- predict(model, test, type='response')
roc.curve(test$Success, logistic_predictions, plotit = TRUE, col = "blue")
```

```{r}
fitted.results <- predict(model, newdata=subset(test, select = c(2,3,4,5,6,7,8)), type='response')
fitted.results <- ifelse(fitted.results > 0.5,1,0)

mis_error <-mean(fitted.results !=test$Success)
print(paste('Accuracy', 1-mis_error))

```